A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-30 paper.tex
Work in progress
Reference update.

Bio-inspired algorithms have been very successful when used to solve complex
optimization problems, but as their complexity increases so does the computing
power required. One strategy to address this processing need is to use
distributed computing, or the resources available in the cloud to help find the
solution. This strategy gives us elasticity to adjust (increase or reduce) the
computing power to achieve a balance according to the nature of the problem.

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective [X-Z], where each process must wait for the previous task to finish
before continuing. Some architectures address this issue, what distinguishes
us, is that our proposal presents an algorithm designed in its entirety as a
native solution in the cloud, fully distributed, where its processes are
executed in parallel and asynchronously. This technique makes it easy to scale
the computing power according to the complexity required by the problem.

@@

One of the main challenges when designing the algorithm was how to capture the
essence of life by reflecting a population evolution?. In our minds, it was
clear this task requires a combination of simultaneous working forces that
influences the population improvement over time. Our strategy was simple:
divide and conquer, looking into the clouds. Enter cloud-computing: previous
cloud-computing algorithms have proven successful results working in
optimization problems \cite{garcia2021event}.

@@

We must acknowledge the performance time of the DEAP library
\cite{fortin2012deap} is highly efficient and short, due in part because the
processing work execution is on a single processor with multiple cores, where
the communication time is nearly non-existent. In contrast, our algorithm
implementation requires a minimum of five containers and a message queue
server. Even though the container work has proven to be very effective and
efficient [X], we must consider some time was added to our experiments by the
minimal delays (in the thousands of a second magnitude) we used to keep the
process execution relatively random, to mimic how the life-cycle stages work in
nature \cite{read1968system}. As future work, we could test the Life-Cycle
algorithm behavior by eliminating all remaining delays.

>>>>

Bio-inspired algorithms have been very successful when used to solve complex
optimization problems
\cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but as
their complexity increases so does the computing power required
\cite{ontiveros2018high}. One strategy to address this processing need is to
use distributed computing \cite{thain2005distributed}, or the resources
available in the cloud \cite{garcia2013there,eshratifar2019bottlenet} to help
find the solution. This strategy gives us elasticity to adjust (increase or
reduce) the computing power to achieve a balance according to the nature of the
problem \cite{armbrust2010view}.

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective \cite{back1996evolutionary} [X-Z], where each process must wait for
the previous task to finish before continuing. Some architectures address this
issue, what distinguishes us, is that our proposal presents an algorithm
designed in its entirety as a native solution in the cloud, fully distributed,
where its processes are executed in parallel and asynchronously. This technique
makes it easy to scale the computing power according to the complexity required
by the problem.

@@

One of the main challenges when designing the algorithm was how to capture the
essence of life by reflecting a population evolution?. In our minds, it was
clear this task requires a combination of simultaneous working forces that
influences the population improvement over time. Our strategy was simple:
divide and conquer, looking into the clouds. Enter cloud-computing: previous
cloud-computing algorithms have proven successful results working in
optimization problems \cite{valdez2021container,garcia2021event}.

@@

We must acknowledge the performance time of the DEAP library
\cite{fortin2012deap} is highly efficient and short, due in part because the
processing work execution is on a single processor with multiple cores, where
the communication time is nearly non-existent. In contrast, our algorithm
implementation requires a minimum of five containers and a message queue
server. Even though the container work has proven to be very effective and
efficient \cite{merelo2016performance,valdez2021container}, we must consider
some time was added to our experiments by the minimal delays (in the thousands
of a second magnitude) we used to keep the process execution relatively random,
to mimic how the life-cycle stages work in nature \cite{read1968system}. As
future work, we could test the Life-Cycle algorithm behavior by eliminating all
remaining delays.
